---
title: "Palmer Penguins Report"
author: "Rifaldi Iqbal"
date: '2022-05-22'
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Setting Up Environment
Notes : setting up my R environment by loading the 'tidyverse' and 'palmerpenguins' packages.

```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```

## Visualization
Here we will go through a series of visualization

### Flipper and body mass in purple
Here we plot flipper length against body mass

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g), color = 'blue') +
  geom_smooth(mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
  xlab("Flipper Length (mm)") +
  ylab("Body Mass (g)")
```

### Flipper and body mass by species
Here, we plot flipper length against body mass and look at the breakdown by species

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
geom_point(aes(shape=species,color=species)) +
  geom_smooth(mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
  xlab("Flipper Length (mm)") +
  ylab("Body Mass (g)")
```

### Flipper and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by species and sex

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
geom_point(aes(color=species,
               shape=species)) +
xlab("Flipper Length (mm)") +
ylab("Body Mass (g)") + 
facet_wrap(~sex)

```